---
title: "BIOL390: Assignment 2"
author: "Mitch Lueken"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Results from an Experiment on Plant Growth

**Description:** Results from an experiment to compare yields (as measured by dried weight of plants) obtained under a control and two different treatment conditions.

**Source:** Dobson, A. J. (1983) _An Introduction to Statistical Modelling_. London: Chapman and Hall.

## Analysis

>>Replace the `XXX` in the code below with the necessary R instructions to give the mean values for each factor level of this dataset in a pretty little table. Hint - the comparison and dataset are the same as in the barplot. You will want to use the function (FUN) of `mean`.

`r knitr::kable(aggregate(PlantGrowth$weight, by = list(PlantGrowth$group), mean), "pandoc", col.names = c("Factor Level", "Average Weight"))`

```{r barplot}
boxplot(weight ~ group,                             # compare weight by group
		data = PlantGrowth,                         # built-in data set
		main = "Distribution of Growth Data",       # set title
		las = 1,                                    # rotate y-axis values
        ylab = "Dried weight of plants",            # set y-axis title
		xlab = "Group",                             # set x-axis title
		ylim = c(3,7),                             # set scale of y-axis
		col = c("#005333","#331166","#FF0000"))        # set bar fill colors
```

>>Edit the barplot above so that the y-axis range plotted is from 3 to 7 and change the colors of the bars to something that you find fun.

```{r anova}
knitr::kable(anova(lm(weight ~ group, data = PlantGrowth)), digits = 3, caption = "One-way ANOVA of Plant Growth Data")
```

>>Provide a short summary of the ANOVA analysis summarized above.

The one-way analysis of variance of the different treatment conditions found the result to be significant at the p < 0.05 level. This implies that at least one of the treatments had a measurable impact on plant yield.
